Initial Analysis

### 2020-10-05 Scripts/Initial_Analysis.Rmd

# For upload to github
Clean_Results_Trans %>%
  left_join(Exploited_Species) %>%
  select(1,taxon_name,2:5,fishing_entity,un_sub_region) %>%
  write_csv(.,"Clean_Results_Trans.csv")

@@

### Data For Map (Fig. 1)

@@

## Weighted bar plots

@@

Subregion_Trans_raw_Value %>% 
  select(sub_region,Size_Entity_sum) %>% 
  distinct(sub_region,.keep_all = TRUE) %>% 
  write_csv(.,
            "Table_S1.csv")

>>>>

# For upload to github
# Clean_Results_Trans %>%
#   left_join(Exploited_Species) %>%
#   select(1,taxon_name,2:5,fishing_entity,un_sub_region) %>%
#   write_csv(.,"Clean_Results_Trans.csv")

@@

### Fig. 1 - Data For Map

@@

## Fig. 2 - Weighted bar plots

@@

Subregion_Trans_raw_Value %>% 
  select(sub_region,Size_Entity_sum) %>% 
  distinct(sub_region,.keep_all = TRUE) %>% 
  arrange(Size_Entity_sum)
  # write_csv(.,
            # "Table_S1.csv")
